A pair of co-moving, Sun-like stars with different chemical abundances:\\ a possible signature of copious rocky accretion (needs work)

### 2017-04-19 paper/ms.tex
all abundances to table; cannot center it right
note on what star means
making sense

% packages
\definecolor{cbblue}{HTML}{3182bd}
\usepackage{microtype}  % ALWAYS!
\usepackage{amsmath,amssymb,natbib}
\hypersetup{backref,breaklinks,colorlinks,urlcolor=cbblue,linkcolor=cbblue,citecolor=black}
\graphicspath{{figures/}}

% define macros for text
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\gaia}{\project{Gaia}}
\newcommand{\rave}{\project{\acronym{RAVE}}}
\newcommand{\apogee}{\project{\acronym{APOGEE}}}
\newcommand{\tmass}{\project{\acronym{2MASS}}}
\newcommand{\documentname}{Article}
\newcommand{\sectionname}{Section}
\newcommand{\figname}{Figure}
\newcommand{\eqname}{Equation}
\newcommand{\dr}{\acronym{DR1}}
\newcommand{\tgas}{\acronym{TGAS}}
\newcommand{\etal}{\textit{et al}.}
\newcommand*\elem[1]{\ensuremath{\mathrm{#1}}}
\newcommand{\sunanalog}{\text{HD 240429}}
\newcommand{\bizarreone}{\text{HD 240430}}

@@

\begin{table*}[htpb]
  \centering
  \caption{Astrometric and spectroscopic measurements}
  \label{tab:t2}
  \begin{tabular}{ccc}
\hline\hline
Name & HD 240429 & HD 240430 \\
\hline
Sp Type & G2 & G0 \\
$T_\mathrm{eff}$ & 5878 & 5803 \\
$\log{g}$ & 4.43 & 4.33 \\
$v\sin{i}$ & 1.1 & 2.5 \\
$[\elem{Fe}/\elem{H}]$ & 0.01 & 0.20 \\
$v_r$ & $-21.2$ & $-21.2$ \\
$\varpi$ & $9.35 \pm 0.24$ & $9.41 \pm 0.25$ \\
$\mu_\alpha^*$ & $89.25 \pm 0.66$ & $89.41 \pm 0.69$ \\
$\mu_\delta$  & $-29.68 \pm 0.54$ & $-30.12 \pm 0.52$\\
\hline\hline
\end{tabular}
\end{table*}

@@

% binary-single and binary-binary exchange
Two stars unrelated at birth may end up in a binary system via binary-single scattering event
that results in an exchange of binary member.
In order to estimate the rate at which any binary-single
event will produce a wide binary system such as \sunanalog\ and \bizarreone,
we may consider the rate at which this wide binary will scatter with a field star to
result in an exchange reaction.
The exchange rate for a binary with semi-major axis $a$ is
\begin{eqnarray}
  \sigma_\mathrm{ex} = \frac{640}{81} \pi a^{2} \frac{1}{v^6}
\end{eqnarray}
where $v$ is the incoming velocity $v_i$ in units of critical velocity $v_c$ defined as
\begin{eqnarray}
  v_c^2 = G \frac{m_1 m_2 (m_1 + m_2 + m_3)}{m_3 (m_1 + m_2)} \frac{1}{a}
\end{eqnarray}
when $v \gg 1$ using the impulse approximation (\citealt{Hut:1983aa,Hut:1983ab}),
which is appropriate for wide binaries scattering with field (disk) stars.
If we assume that field stars are made of solar mass stars with constant $n=1$~pc$^{-3}$,
and the incoming velocity is $10$~km\,s$^{-1}$, a lower limit to the velocity dispersions of disk
stars in any direction, the rate of exchange scattering is
\begin{eqnarray}
  n \sigma_\mathrm{ex} v_i = 6.82\times 10^{-8}\,\mathrm{Gyr}^{-1}
  \frac{n}{\mathrm{pc}^3} \frac{\mathrm{pc}}{a} \left(\frac{10~\mathrm{km}\,\mathrm{s}^{-1}}{v_i}\right)^5
\end{eqnarray}
low enough to be negligible.

>>>>

% packages
\definecolor{cbblue}{HTML}{3182bd}
\usepackage{microtype}  % ALWAYS!
\usepackage{amsmath,amssymb,natbib}
\usepackage[flushleft]{threeparttable}
\hypersetup{backref,breaklinks,colorlinks,urlcolor=cbblue,linkcolor=cbblue,citecolor=black}
\graphicspath{{figures/}}

% define macros for text
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\gaia}{\project{Gaia}}
\newcommand{\rave}{\project{\acronym{RAVE}}}
\newcommand{\apogee}{\project{\acronym{APOGEE}}}
\newcommand{\tmass}{\project{\acronym{2MASS}}}
\newcommand{\documentname}{Article}
\newcommand{\sectionname}{Section}
\newcommand{\figname}{Figure}
\newcommand{\eqname}{Equation}
\newcommand{\dr}{\acronym{DR1}}
\newcommand{\tgas}{\acronym{TGAS}}
\newcommand{\etal}{\textit{et al}.}
\newcommand*\elem[1]{\ensuremath{\mathrm{#1}}}
\newcommand*\elemH[1]{\ensuremath{[\mathrm{#1}/\elem{H}]}}
\newcommand{\sunanalog}{\text{HD 240429}}
\newcommand{\bizarreone}{\text{HD 240430}}

@@

\begin{table*}[htpb]
  \caption{Astrometric and spectroscopic measurements.}
  \label{tab:t2}
  \begin{threeparttable}
  \centering
  \begin{tabular}{ccc}
\hline\hline
Name & HD 240429 & HD 240430 \\
\hline
Sp Type                                   & G2                & G0                \\
$T_\mathrm{eff}$                          & 5878              & 5803              \\
$\log{g}$                                 & 4.43              & 4.33              \\
$v\sin{i}$                                & 1.1               & 2.5               \\
$[\elem{Fe}/\elem{H}]$                    & 0.01              & 0.20              \\
$v_r$                                     & $-21.2$           & $-21.2$           \\
$\varpi$ \footnotemark[1]                 & $9.35 \pm 0.24$   & $9.41 \pm 0.25$   \\
$\mu_\alpha^*$ \footnotemark[1]           & $89.25 \pm 0.66$  & $89.41 \pm 0.69$  \\
$\mu_\delta$ \footnotemark[1]             & $-29.68 \pm 0.54$ & $-30.12 \pm 0.52$ \\
\hline
\multicolumn{3}{c}{$T_c < 1200$~K} \\
\hline
$\elemH{Li}_*$ \footnotemark[2]           & $2.25$            & $2.75$            \\
$\elemH{C}$                               & $0.00$            & $0.09$            \\
$\elemH{N}$                               & $-0.06$           & $-0.01$           \\
$\elemH{O}$                               & $0.01$            & $0.09$            \\
$\elemH{Na}$                              & $-0.06$           & $-0.04$           \\
$\elemH{Mn}$                              & $-0.03$           & $0.00$            \\
\hline
\multicolumn{3}{c}{$T_c > 1200$~K} \\
\hline
$\elemH{Mg}$                              & $0.01$            & $0.19$            \\
$\elemH{Al}$                              & $0.01$            & $0.21$            \\
$\elemH{Si}$                              & $0.00$            & $0.16$            \\
$\elemH{Ca}$                              & $0.02$            & $0.23$            \\
$\elemH{Ti}$                              & $0.02$            & $0.20$            \\
$\elemH{V}$                               & $0.02$            & $0.20$            \\
$\elemH{Cr}$                              & $0.01$            & $0.17$            \\
$\elemH{Fe}$                              & $0.01$            & $0.20$            \\
$\elemH{Ni}$                              & $-0.01$           & $0.21$            \\
$\elemH{Y}$                               & $0.04$            & $0.26$            \\
\hline\hline
\end{tabular}
%
\begin{tablenotes}
  \item All spectroscopic measurements except $\elem{Li}$ are from \citealt{2016ApJS..225...32B}.
  \footnotetext[1]{From \tgas. }
  \footnotetext[2]{Absolute abundance from \todo{CITE}.}
\end{tablenotes}
  \end{threeparttable}
\end{table*}

@@

% binary-single and binary-binary exchange
Two stars unrelated at birth may end up in a binary system via binary-single scattering event
that results in an exchange of binary member.
In order to estimate the rate at which any binary-single
event will produce a wide binary system such as \sunanalog\ and \bizarreone,
we may consider the rate at which this wide binary will scatter with a field star to
result in an exchange reaction.
The cross-section of exchange scattering for a binary with semi-major axis $a$ is
\begin{eqnarray}
  \sigma_\mathrm{ex} = \frac{640}{81} \pi a^{2} \frac{1}{v^6}
\end{eqnarray}
where $v$ is the incoming velocity $v_i$ in units of critical velocity $v_c$ defined as
\begin{eqnarray}
  v_c^2 = G \frac{m_1 m_2 (m_1 + m_2 + m_3)}{m_3 (m_1 + m_2)} \frac{1}{a}
\end{eqnarray}
when $v \gg 1$ using the impulse approximation (\citealt{Hut:1983aa,Hut:1983ab}),
which is appropriate for wide binaries scattering with field (disk) stars.
If we assume that field stars are made of solar mass stars
with constant number density $n=1$~pc$^{-3}$, and the incoming velocity of field stars
is $10$~km\,s$^{-1}$, a lower limit to the velocity dispersions of disk
stars in any direction, the rate of exchange scattering is
\begin{eqnarray}
  n \sigma_\mathrm{ex} v_i = 6.82\times 10^{-8}\,\mathrm{Gyr}^{-1}
  \frac{n}{\mathrm{pc}^3} \frac{\mathrm{pc}}{a} \left(\frac{10~\mathrm{km}\,\mathrm{s}^{-1}}{v_i}\right)^5
\end{eqnarray}
low enough to be negligible.
